\documentclass[onecolumn,nocopyrightspace,preprint]{sigplanconf}

\usepackage{booktabs}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{caption}
\usepackage[tocentry]{vhistory}

% \lstset{
%   commentstyle=\small\ttfamily, %
%   fontadjust=true, %
%   firstnum  ber=1, %
%   escapeinside={(*}{*)}, %
% }

\lstset{
  float=*,
  numbers=none,
  numberstyle=\footnotesize,
  numbersep=4pt,
  basicstyle=\small\ttfamily,
  keywordstyle=\small\ttfamily\bf,
  tabsize=2,
  breaklines=true,
  frame=lines,
  aboveskip=\bigskipamount,
  belowskip=\bigskipamount,
  %belowcaptionskip=\medskipamount,
  language=bash,
  deletekeywords={env, for}
}

\nocaptionrule



\title{Antescofo: Project Title}
\authorinfo{
  Martin~Aigner
}{University of Salzburg}{firstname.lastname@cs.uni-salzburg.at}

\begin{document}
\maketitle
%\tableofcontents

\section*{Foreword} 
Writing this report is part of the requirements of [CLASSNAME] intended to
make students think about combining different topics of education through
a single common property: the use of computers.

Say here, that this is important because...

The goal is to propose a hypothetical project.

The cool thing here: this project actually actually happened.

\section*{Abstract} 

(Context) Our research group is involved in a research project on Antescofo, a
real-time multimedia system, developed by IRCAM, Paris. Antescofo is a complex
piece of software used to accompany musicians and orchestras on the stage. It
is used at various concert halls throughout the world, including the
Festspielhaus in Salzburg. We have recently submitted a research proposal with
IRCAM on advancing the real-time aspects of Antescofo for embedded devices.

(Internship) The task of the students within this internship is to setup, use,
(and so performance analysis of Antescofo. Some of the challenges of Antescofo
(are scalability, as well as proper modelling of time, topics that our
(research group has expertise on. The students are expected to get Antescofo
(running in a lab environment, demonstrate simple use with an actual
(instrument, and isolate performance issues that motivate our research). This
(internship project will be a valuable kick-off for our research on enhancing
(the real-time aspects of Antescofo.

(technical bla-bla) Assets for the students: experience working on a highly
(sophisticated software system; get acquainted with technical issues of
(setting up a system; experience with performance analysis and with research
(on real-time aspects of computing; fun with music and complex software.


\end{document}


